\headingfont UNIVERSIDAD DE EXTREMADURA\\ FACULTAD DE CIENCIAS\\[1.5cm] \textbf{ Grado en Física\\ TRABAJO DE FIN DE GRADO\\[3.5cm]} {\setstretch{1.25}\flushleft{\large{\textbf{Developement of a FIWARE-based application for tree species monitoring (dendrometry)}}\\[3.5cm]}}

### 2020-07-06 docs/LaTex/Paper.tex
Fixes a typo

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}  % Forces the next section to start in an odd page.
\section{Proof of concept, deployment}
Due to inconvenient circumstances at early 2020, this section is not as long as initially planted, instead of testing the system in a real production environment, this section will focus on summarizing needed steps/stages to properly deploy the system. Although these steps are already separately detailed, this section tries to put them together to give a consistent and practical point of view.

>>>>

\clearpage{\pagestyle{empty}\cleardoublepage}\thispagestyle{plain}  % Forces the next section to start in an odd page.
\section{Proof of concept, deployment}
Due to inconvenient circumstances at early 2020, this section is not as long as initially planned, instead of testing the system in a real production environment, this section will focus on summarizing needed steps/stages to properly deploy the system. Although these steps are already separately detailed, this section tries to put them together to give a consistent and practical point of view.
